\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-03 paper.qmd
Added scratch writing for the best and bad models

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>).
:::

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/DHPvhkZ0lUM>).
:::

@@

<!--bad model-->
<!--need to mention why it is the bad-->
<!--Not represented the whole data structure beacuse there are some discontinuity in the S-curve-->
<!-- Why? bad

>>>>

The best model for the S-curve with UMAP (n_neighbors: $15$) create with $420$ of total number of bins. Also, the best model made after removing edges which has the length greater than $0.134$. Why this is the best? Because AIC plot shows that the minimum occur at $420$. Visually, the model capture the geometry of the S-curve well.

On the other hand, a bad model for the S-curve with UMAP is made with $190$ bins, and removing edges which has the length greater than $0.3$. Why this is a bad model? The MSE error is greater than the best model. Visually, the model is not continuously fitted along with the S-curve data, and show some disconnect edges.

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>). MSE with $0.035$.
:::

@@

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/DHPvhkZ0lUM>). MSE with $0.090$.
:::

@@

<!--bad model-->
<!--need to mention why it is the bad-->
<!--Not represented the whole data structure because there are some discontinuity in the S-curve-->
<!-- Why? bad

### 2024-06-03 paper.tex
Added scratch writing for the best and bad models

>>>>

The best model for the S-curve with UMAP (n\_neighbors: \(15\)) create
with \(420\) of total number of bins. Also, the best model made after
removing edges which has the length greater than \(0.134\). Why this is
the best? Because AIC plot shows that the minimum occur at \(420\).
Visually, the model capture the geometry of the S-curve well.

On the other hand, a bad model for the S-curve with UMAP is made with
\(190\) bins, and removing edges which has the length greater than
\(0.3\). Why this is a bad model? The MSE error is greater than the best
model. Visually, the model is not continuously fitted along with the
S-curve data, and show some disconnect edges.

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_3.png}\end{minipage}%

\caption{\label{fig-scurve_sc}Screen shots of the \textbf{langevitour}
of the S-curve, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/4RFNENX_fXk}). MSE with
\(0.035\).}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_3.png}\end{minipage}%

\caption{\label{fig-scurve_sc}Screen shots of the \textbf{langevitour}
of the S-curve, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/DHPvhkZ0lUM}). MSE with
\(0.090\).}
